{\normalsize \textbf{Vagueness and imprecise imitation in signalling games}}

### 2016-06-09 paper/version_final/paper.tex
Added reference to PhD grant.

We would like to thank Gerhard J\"{a}ger and several anonymous reviewers for their insightful comments and suggestions on
earlier versions of this paper. Funding for this research was provided by the Dutch Research
Council (NWO-VENI grant 275-80-004 to Michael Franke), the Institutional Strategy of the
University of T\"{u}bingen (German Research Foundation ZUK 63 to Michael Franke), and the Priority
Program XPrag.de (German Research Foundation Schwerpunktprogramm 1727 to Michael Franke).

>>>>

We would like to thank Gerhard J\"{a}ger and several anonymous reviewers for their insightful comments and suggestions on
earlier versions of this paper. Funding for this research was provided by the Dutch Research
Council (NWO-VENI grant 275-80-004 to Michael Franke), the Institutional Strategy of the
University of T\"{u}bingen (German Research Foundation ZUK 63 to Michael Franke), the Priority
Program XPrag.de (German Research Foundation Schwerpunktprogramm 1727 to Michael Franke), and the Fundação para a Ciência	e a Tecnologia (PhD studentship SFRH/BD/100437/2014 to José Pedro Correia).
